\include{zinput} \begin{document}\section{{\tt zeligDepUpdate}: Download Zelig Dependencies Packages}\label{ss:zeligDepUpdate}
\keyword{documentation}{zeligDepUpdate}
\begin{Description}\relax
Compares the packages in Zelig-matrix of dependencies  to the
locally installed packages. Finds local packages that have lower
versions than in the corresponding row of the Zelig-matrix.
Also, finds packages that \pkg{Zelig} required but are not
installed locally.
Downloads packages that are locally installed with lower versions and
those from the Zelig-matrix that are not installed.
The download repository is taken from either the default
\code{\var{repos}} argument or from the \sQuote{URL} column of
the Zelig-matrix of dependencies.
\end{Description}
\begin{Usage}
\begin{verbatim}
zeligDepUpdate(destdir = NULL, installWithVers = FALSE, lib.loc = NULL,
repos = "http://cran.r-project.org")
\end{verbatim}
\end{Usage}
\begin{Arguments}
\begin{ldescription}
\item[\code{destdir}] directory to store the compress source-codes of
packages that are downloaded from web repositories.
\item[\code{installWithVers}] if TRUE, will invoke the install of the
package such that it can be referenced by package version.
\item[\code{lib.loc}] character vector describing the location of R
library trees to search through (and update packages therein). 
\item[\code{repos}] character vector, the base URL(s) of the repositories to
use, i.e. the URL of the CRAN master such as
"http://cran.r-project.org", which is the default, or its Statlib
mirror, "http://lib.stat.cmu.edu/R/CRAN". Can be NULL to install
from local zip files.
\end{ldescription}
\end{Arguments}
\begin{Value}
No return value.
\end{Value}
\begin{Note}\relax
Installs first level dependencies packages of \pkg{Zelig} using R function
\code{install.packages} with the variable \code{\var{dependencies}} set
equal to TRUE.  If the installed packages have versions higher than the
corresponding entry in Zelig-matrix, they are reported with a
message. If the R version in the local environment is different from
the R version that \pkg{Zelig} depends on, then, it is reported with a message and no futher action is taken.
\end{Note}
\begin{Author}\relax
Ferdinand Alimadhi and Elena Villalon
\end{Author}
\begin{References}\relax
King, Gary. Zelig: Everyones Statistical Software. 
\url{http://gking.harvard.edu/zelig}.
\end{References}
\begin{SeeAlso}\relax
\code{\LinkA{zeligDepStatus}{zeligDepStatus}}
\code{\LinkA{install.packages}{install.packages}}
\end{SeeAlso}
\begin{Examples}
\begin{ExampleCode}
##checks all libraries curently know for packages
## Not run: zeligDepUpdate()
##finds packages only in lib.loc
## Not run: zeligDepUpdate(lib.loc="~/.R/mylibrary")
\end{ExampleCode}
\end{Examples}

\end{document}
