\include{zinput} \begin{document}\section{{\tt zeligDepStatus}: Zelig Dependencies Packages Client Status}\label{ss:zeligDepStatus}
\keyword{documentation}{zeligDepStatus}
\begin{Description}\relax
Compares Zelig-matrix of dependencies to the locally installed
packages. Finds those packages that \pkg{Zelig} depends on and are not
installed in local environment. Also finds those packages that are
locally installed but with lower versions than those required in the
dependencies matrix.
The Zelig-matrix includes any of dependency fields in the
\sQuote{DESCRIPTION} files, i.e. depends, imports and suggests,
for any packages directly derived from \pkg{Zelig} and for any of the models that \pkg{Zelig} supports.
\end{Description}
\begin{Usage}
\begin{verbatim}
zeligDepStatus(lib.loc = NULL)
\end{verbatim}
\end{Usage}
\begin{Arguments}
\begin{ldescription}
\item[\code{lib.loc}] a character vector of directory names 
of \code{R} libraries, or NULL.
The default value NULL corresponds to all libraries currently known. If the default is used, the loaded packages are searched before the libraries. 
\end{ldescription}
\end{Arguments}
\begin{Value}
Returns a matrix of packages that are either installed locally 
with lower versions, or packages not installed but listed in the
Zelig-matrix of dependencies.  The matrix rows correspond to the packages and 
the columns contain the following fields
\begin{ldescription}
\item[\code{Package}] names of packages.
\item[\code{Version}] versions locally installed
\item[\code{Zideal}] versions required in Zelig-matrix of dependencies.
\end{ldescription}
\end{Value}
\begin{Note}\relax
If the R version in the local environment is different from the R
version that \pkg{Zelig}  
depends on, then, it is reported with a message and no futher action is taken. 
If the installed packages have versions higher than the corresponding 
values in the Zelig-matrix, it is reported with a message.
\end{Note}
\begin{Author}\relax
Ferdinand Alimadhi and Elena Villalon
\end{Author}
\begin{References}\relax
King, Gary. Zelig: Everyones Statistical Software. 
\url{http://gking.harvard.edu/zelig}.
\end{References}
\begin{SeeAlso}\relax
\code{\LinkA{installed.packages}{installed.packages}}
\code{\LinkA{packageDescription}{packageDescription}}
\code{\LinkA{zeligDepUpdate}{zeligDepUpdate}}
\end{SeeAlso}
\begin{Examples}
\begin{ExampleCode}
## find packages in all libraries currently installed
## Not run: zstatus <- zeligDepStatus()
## find packages only in lib.loc
## Not run: zstatus <- zeligDepStatus(lib.loc="~/.R/mylibrary")
\end{ExampleCode}
\end{Examples}

\end{document}
