\include{zinput} \begin{document}\section{{\tt zeligDescribeModelXML}: Zelig interface functions}\label{ss:zeligDescribeModelXML}
\aliasA{zeligGetSpecial}{zeligDescribeModelXML}{zeligGetSpecial}
\aliasA{zeligInstalledModels}{zeligDescribeModelXML}{zeligInstalledModels}
\aliasA{zeligListModels}{zeligDescribeModelXML}{zeligListModels}
\aliasA{zeligModelDependency}{zeligDescribeModelXML}{zeligModelDependency}
\keyword{IO}{zeligDescribeModelXML}
\keyword{print}{zeligDescribeModelXML}
\begin{Description}\relax
Zelig interface functions. Used by VDC DSB to  communicate with Zelig.
\end{Description}
\begin{Usage}
\begin{verbatim}
        zeligDescribeModelXML(modelName,force=FALSE,schemaVersion="1.1")
        zeligInstalledModels(inZeligOnly=TRUE,schemaVersion="1.1")
        zeligListModels(inZeligOnly=TRUE) 
        zeligModelDependency(modelName,repos) 
        zeligGetSpecial(modelName)
\end{verbatim}
\end{Usage}
\begin{Arguments}
\begin{ldescription}
\item[\code{modelName}] Name of model as returned by zeligInstalledModels or zeligListModels.
\item[\code{inZeligOnly}] Flag, include only models in official Zelig distribution
\item[\code{repos}] URL of default repository to use
\item[\code{schemaVersion}] version of Zelig schema
\item[\code{force}] generate a description even if no custom description supplied
\end{ldescription}
\end{Arguments}
\begin{Value}
Use zeligInstalledModels and zeligListModels to determine what models are available in zelig
for a particular schema level. Use zmodel2string(zeligDescribeModel()) to generate an XML
instance describing a model. Use zeligModelDependencies to generate a list of package
dependencies for models. Use zeligGetSpecial to get the name special function, if any,
to apply to the outcome variables. All functions return NULL if results are
not available for that model.
\end{Value}
\begin{Author}\relax
Micah Altman
\email{thedata-users\@lists.sourceforge.net}
\url{http://thedata.org}
\end{Author}
\begin{SeeAlso}\relax
\LinkA{zelig}{zelig}
\end{SeeAlso}
\begin{Examples}
\begin{ExampleCode}## Not run: 
        # show all available models
        zeligListModels(inZeligOnly=FALSE)
        # show installed models
        zeligInstalledModels()
        # show dependency for normal.bayes
        zeligModelDependency("normal.bayes","http://cran.r-project.org/")
        # description of logit
        cat(zeligDescribeModelXML("ologit"))
        # special function for factor analysis
        zeligGetSpecial("factor.mix")
## End(Not run)


\end{ExampleCode}
\end{Examples}

\end{document}
